Conference Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2021-03-13 paper/main.tex
summary

\section{Introduction}
Nowadays, keeping track of the domestic energy usage is a common scenario in domotic applications that aim to monitor the real-time watt consumption of home appliances. In most cases the solution is a sensor connected to the main safety switch yielding the total energy consumption. Our approach, to get more detailed information and to have control on the use of power by the appliances, is to have an energy sensor for each plug connected to the 220V line. In the following paragraphs, we present our \textit{proof of concept} (POC) which, functionally, consists of three main components: the smart plugs, the main server and the web interface. In our POC, we have modified the architecture described in \cite{8110428} obtaining a specific low-energy consume-driven infrastructure. This consists of: the smart plugs, a central processing unit (for the main server) and a device (for the web interface). In a home scenario these devices are connected to the home wireless router. The communication between smart plugs and server occur over UDP with a simple form of reliability implemented at the application level. The smart plugs have been prototyped using Arduino and the server has been written in Java. Let's now consider a use case example: the user sets the maximum power consumption possible in the home and then turns on two appliances. When this happens for the first time the system decides, based on the type of appliance connected, a default value for the maximum power usage of the appliance. This value is then updated to reflect the real maximum power usage of the appliance. Now that the system is running and some appliances are turned on, the user will be able to switch on only the appliances that consume less then the available power. Our POC covers this use case and shows that such a system can be practical and useful and that the traffic generated isn't enough to sensibly worsen the performances of the typical home WLAN. To summarize, the system keeps the power usage from reaching the maximum limit set by the user by forbidding the power on of appliances that consume more then the available power. It also gives granular information about the devices consumption and allows the user to turn on or off appliances remotely (via web interface). Aside from the main use case, in the age of climate awareness, such a system could be interesting to an environmentally conscious user that can monitor the power usage of appliances but also could set the maximum power consumption to be lower then the real one in order to use less power or save money.

@@

The smart plugs have been prototyped using Arduino. The module drives a sensor, needed to gather data on the power consumption and communicates with the UDP server 
\par After describing some architectural design aspects,%

>>>>

\section{Introduction}
Nowadays, keeping track of the domestic energy usage is a common scenario in domotic applications that aim to monitor the real-time watt consumption of home appliances. In most cases the solution is a sensor connected to the main safety switch yielding the total energy consumption. Our approach, to get more detailed information and to have control on the use of power by the appliances, is to have an energy sensor for each plug connected to the 220V line. In the following paragraphs, we present our \textit{proof of concept} (POC) which, functionally, consists of three main components: the smart plugs, the main server and the web interface. In our POC, we have modified the architecture described in \cite{8110428} obtaining a specific low-energy consume-driven infrastructure. This consists of: the smart plugs, a central processing unit (for the main server) and a device (for the web interface). In a home scenario these devices are connected to the home wireless router. The communication between smart plugs and server occur over UDP with a simple form of reliability implemented at the application level, and tested using Wireshark \cite{wireshark}. The smart plugs have been prototyped using Arduino and the server has been written in Java. Let's now consider a use case example: the user sets the maximum power consumption possible in the home and then turns on two appliances. When this happens for the first time the system decides, based on the type of appliance connected, a default value for the maximum power usage of the appliance. This value is then updated to reflect the real maximum power usage of the appliance. Now that the system is running and some appliances are turned on, the user will be able to switch on only the appliances that consume less then the available power. Our POC covers this use case and shows that such a system can be practical and useful and that the traffic generated isn't enough to sensibly worsen the performances of the typical home WLAN. To summarize, the system keeps the power usage from reaching the maximum limit set by the user by forbidding the power on of appliances that consume more then the available power. It also gives granular information about the devices consumption and allows the user to turn on or off appliances remotely (via web interface). Aside from the main use case, in the age of climate awareness, such a system could be interesting to an environmentally conscious user that can monitor the power usage of appliances but also could set the maximum power consumption to be lower then the real one in order to use less power or save money.

@@

The smart plugs have been prototyped using Arduino. The module drives a sensor, needed to gather data on the power consumption and communicates with the UDP server 
\par After describing some architectural design aspects,
\subsection{Smart plugs}\label{SP}
\subsection{Server}\label{SVR}
\subsection{Web interface}\label{WI}

\section{System results}
\section{Consumption}
%Qui mettiamo workflow generale con immagine algoritmo
